---
title: "Madison Observations"
author: "Ruth Enriquez"
date: "2022-08-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

```{r}
ice_duration_data <- read_csv(here("data", "ntl33_v7.csv"), na = c("-999"))

meteoro_data <- read_csv(here("data", "ntl20_v6.csv"))
```

-   Create a visualization that compares ice duration across different lakes in the Madison Lake Area. Include both the actual ice duration values *and* some representation of summary statistics for each lake. Careful if you use a boxplot over a jitter or beeswarm - what values might be doubly represented? Can you find an argument that would help you remove those from the boxplot?

```{r}
ggplot(data = ice_duration_data, aes(x = lakeid,
                                     y = ice_duration)) +
  geom_jitter(width = 0.2) +
  geom_boxplot(width = 0.3, fill = NA, size = 1, outlier.colour = NA)
```

-   Find the mean ice cover duration in Madison Lake Area by year (i.e., you\'ll only be grouping by the year variable here). Understanding check: what are you finding the mean of here? Why are there multiple observations for each year?)

```{r}
mean_duration <- ice_duration_data |> 
  group_by(year4) |> 
  mutate(mean_ice = mean(ice_duration))
```
